Stool Microbiome Analysis

### 2022-02-02 Rmarkdown/analysis/Fecal_Microbiome_TMAO_Analysis_211105.Rmd
Loop plot and name changes

# Loop Plot
nres <- length(resOTU)
for (i in 1:nres) { 
    print(ggplot(ggData, aes(x = tmao_tertile, y = log(ggData[,i]))) +
            geom_boxplot()+
            ylab(colnames(ggData)[i])) 
}

@@

# Merge
ggData <- merge(taxaData_res, otuData_desRes, by = 0)
rownames(ggData) <-  ggData$OrderFamily
ggData <- ggData[,-(1:9)]
ggData <- as.data.frame(t(ggData))
ggData <- merge(ggData, sampleData, by = 0)
rownames(ggData) <- ggData[,"Row.names"]
ggData <- subset(ggData, select = -c(Row.names))

# Loop Plot
nres <- length(resOTU)
for (i in 1:nres) { 
    print(ggplot(ggData, aes(x = tmao_tertile, y = log(ggData[,i]))) +
            geom_boxplot(aes(color=tmao_tertile)) +
            geom_point() +
            theme_minimal() +
            ylab(paste0("Log of", colnames(ggData[i]))) +
            xlab("TMAO Tertile") +
            scale_color_brewer(palette = "Dark2") +
            labs(color = "TMAO Tertile")
    )
}

# Loop Plot
nres <- length(resOTU)
for (i in 1:nres) { 
    temp_plot <- ggplot(ggData, aes(x = tmao_tertile, y = log(ggData[,i]))) +
            geom_boxplot(aes(color=tmao_tertile)) +
            geom_point() +
            theme_minimal() +
            ylab(paste0("Log of", colnames(ggData[i]))) +
            xlab("TMAO Tertile") +
            scale_color_brewer(palette = "Dark2") +
            labs(color = "TMAO Tertile")
    tiff(paste0("../../Outputs/plots/microbiome/DESeq2_Family_TMAOTertile_Boxplot_", i,"_2201.tiff"), width = 4, height = 4, units = 'in', res = 300)
    print(temp_plot)
    dev.off()
}

>>>>

#~~~~~~~~~~~~~~~
# Plot Results
#~~~~~~~~~~~~~~~
resOTU <- rownames(sigtab)
otuData <- as.data.frame(otu_table(PSOtmao1G))
otuData_desRes <- otuData[rownames(otuData) %in% resOTU,]
#otuData_desRes <- as.data.frame(t(otuData_desRes))
# Get sample data groupings
sampleData <- as.data.frame(sample_data(PSOtmao1G))
sampleData <- subset(sampleData, select = c(tmao_mdn, tmao_quantile, tmao_tertile, tmao))
# Get tax table
taxaData <- as.data.frame(tax_table(PSOtmao1G))
taxaData_res <- taxaData[rownames(taxaData) %in% resOTU,]
taxaData_res$FamilyGenus <- paste0(taxaData_res$Family, taxaData_res$Genus)

# Merge
ggData <- merge(taxaData_res, otuData_desRes, by = 0)
rownames(ggData) <-  ggData$FamilyGenus
ggData <- ggData[,-(1:9)]
ggData <- as.data.frame(t(ggData))
ggData <- merge(ggData, sampleData, by = 0)
rownames(ggData) <- ggData[,"Row.names"]
ggData <- subset(ggData, select = -c(Row.names))
# Save a copy of results for plotting
ggData_G <- ggData

# Loop Plot to view
nres <- length(resOTU)
comparisons <- list(c("Tertile1", "Tertile2"), c("Tertile1", "Tertile3"), c("Tertile2","Tertile3"))
for (i in 1:nres) { 
    print(ggplot(ggData_G, aes(x = tmao_tertile, y = log(ggData_G[,i]))) +
            geom_boxplot(aes(color=tmao_tertile)) +
            geom_point() +
            theme_minimal() +
            ylab(paste0("Log of", colnames(ggData_G[i]))) +
            xlab("TMAO Tertile") +
            scale_color_brewer(palette = "Dark2") +
            labs(color = "TMAO Tertile") +
            stat_compare_means(comparisons=comparisons)
    )
}

# Loop Plot to save
nres <- length(resOTU)
comparisons <- list(c("Tertile1", "Tertile2"), c("Tertile1", "Tertile3"), c("Tertile2","Tertile3"))
for (i in 1:nres) { 
    temp_plot <- ggplot(ggData_G, aes(x = tmao_tertile, y = log(ggData_G[,i]))) +
            geom_boxplot(aes(color=tmao_tertile)) +
            geom_point() +
            theme_minimal() +
            ylab(paste0("Log of \n", colnames(ggData_G[i]))) +
            xlab("TMAO Tertile") +
            scale_color_brewer(palette = "Dark2") +
            labs(color = "TMAO Tertile") 
            #stat_compare_means(comparisons=comparisons)
    tiff(paste0("../../Outputs/plots/microbiome/DESeq2_Genus_TMAOTertile_Boxplot_", i,"_2201.tiff"), width = 4, height = 4, units = 'in', res = 300)
    print(temp_plot)
    dev.off()
}

@@

# Merge
ggData <- merge(taxaData_res, otuData_desRes, by = 0)
rownames(ggData) <-  ggData$OrderFamily
ggData <- ggData[,-(1:9)]
ggData <- as.data.frame(t(ggData))
ggData <- merge(ggData, sampleData, by = 0)
rownames(ggData) <- ggData[,"Row.names"]
ggData <- subset(ggData, select = -c(Row.names))
# Save a copy of results for plotting
ggData_F <- ggData

# Loop Plot to view
nres <- length(resOTU)
for (i in 1:nres) { 
    print(ggplot(ggData_F, aes(x = tmao_tertile, y = log(ggData_F[,i]))) +
            geom_boxplot(aes(color=tmao_tertile)) +
            geom_point() +
            theme_minimal() +
            ylab(paste0("Log of", colnames(ggData_F[i]))) +
            xlab("TMAO Tertile") +
            scale_color_brewer(palette = "Dark2") +
            labs(color = "TMAO Tertile")
    )
}

# Loop Plot to save
nres <- length(resOTU)
for (i in 1:nres) { 
    temp_plot <- ggplot(ggData_F, aes(x = tmao_tertile, y = log(ggData_F[,i]))) +
            geom_boxplot(aes(color=tmao_tertile)) +
            geom_point() +
            theme_minimal() +
            ylab(paste0("Log of", colnames(ggData_F[i]))) +
            xlab("TMAO Tertile") +
            scale_color_brewer(palette = "Dark2") +
            labs(color = "TMAO Tertile")
    tiff(paste0("../../Outputs/plots/microbiome/DESeq2_Family_TMAOTertile_Boxplot_", i,"_2201.tiff"), width = 4, height = 4, units = 'in', res = 300)
    print(temp_plot)
    dev.off()
}
